Physcraper: A Python package for continually updated phylogenetic trees using the Open Tree of Life

### 2021-05-01 sources/bmc_template_submission/bmc_article.tex
more tiny edits

%%%%%%%%%%%%%%%%
%% Background %%
%%
\section*{Background}
Phylogenies capture the shared history of organisms and provide key evolutionary
context for our biological observations \cite{dobzhansky1973nothing}.
Updating existing phylogenies with publicly available molecular sequence data provides
the opportunity to simultaneously study
the evolutionary history of many taxa in a reproducible and continuous manner.
Increased taxonomic sampling improves
phylogenetic reconstructions \cite{hillis1996inferring, natsidis2019phylogenomics},
time of divergence estimates \cite{schulte2013undersampling, soares2015influence},
and biogeographic analyses \cite{kayaalp2017back},
and help in resolving phylogenetic conflict \cite{hedtke2006resolution, townsend2010optimal, natsidis2019phylogenomics}.
Here, we introduce Physcraper, a Python package that provides a data interoperability
framework to automate data connections across biological databases,
with the main goal to build upon published alignments and phylogenies
to extend existing phylogenetic inferences with sequence data available for more taxa
in public DNA databases.
% Physcraper updates the starting single locus alignment and corresponding phylogeny
% with public DNA data from GenBank \cite{benson2000genbank}, and links tip taxon
% labels in the updated trees to a unified, interoperable
% taxonomic resource \cite{rees2017automated}, streamlining connections between phylogenies and biological data.
Physcraper links tip taxon labels in the updated trees to a unified, interoperable
taxonomic resource \cite{rees2017automated}, effectively streamlining connections
between phylogenies and any type of biological data.

>>>>

%%%%%%%%%%%%%%%%
%% Background %%
%%
\section*{Background}
Phylogenies capture the shared history of organisms and provide key evolutionary
context for our biological observations \cite{dobzhansky1973nothing}.
Updating existing phylogenies with publicly available molecular sequence data provides
the opportunity to simultaneously study
the evolutionary history of many taxa in a reproducible and continuous manner.
Increased taxonomic sampling is known to improve
phylogenetic reconstructions \cite{hillis1996inferring, natsidis2019phylogenomics},
time of divergence estimates \cite{schulte2013undersampling, soares2015influence},
and biogeographic analyses \cite{kayaalp2017back},
as well as help in resolving phylogenetic conflict \cite{hedtke2006resolution, townsend2010optimal, natsidis2019phylogenomics}.
Here, we introduce Physcraper, a Python package that provides a data interoperability
framework to automate data connections across biological databases,
with the main goal of building upon published alignments and phylogenies
to extend existing phylogenetic inferences with sequence data available for more taxa
in public DNA databases.
% Physcraper updates the starting single locus alignment and corresponding phylogeny
% with public DNA data from GenBank \cite{benson2000genbank}, and links tip taxon
% labels in the updated trees to a unified, interoperable
% taxonomic resource \cite{rees2017automated}, streamlining connections between phylogenies and biological data.
Physcraper links tip taxon labels in the updated trees to a unified, interoperable
taxonomic resource \cite{rees2017automated}, effectively streamlining connections
between phylogenies and any type of biological data.
